### 2013-04-16 R/reportmd.Rmd
every possible combination of plots added, added a small change to Baraloto2006's latitude because the original coordinate provided was too close to the sea and the package maps was not able to recognize the country

**Location dtaa**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

@@

This is how the study `r .study` (red symbols) fits in the entire dataset.

>>>>

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

@@

This is how the study `r .study` (each color represents a species) fits in the entire dataset (grey).
